A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Emphasize t in t-test

We conducted a two-sample Welch t-test to compare the average bill lengths between male and female penguins.
The null hypothesis ($H_0$) states that there is no difference in bill lengths between male and female penguins, while the alternative hypothesis ($H_1$) suggests a significant difference.

The t-test was performed using the `t.test()` function in R, with a significance level of 0.05.

@@

The t-test revealed a significant difference in bill lengths between male and female penguins ($t(`r round(t_test_result$parameter, digits = 2)`) = `r round(t_test_result$statistic, digits = 2)`{,}\> p `r format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `r round(mean(blm_female), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `r round(mean(blm_male), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).

>>>>

We conducted a two-sample Welch *t*-test to compare the average bill lengths between male and female penguins.
The null hypothesis ($H_0$) states that there is no difference in bill lengths between male and female penguins, while the alternative hypothesis ($H_1$) suggests a significant difference.

The *t*-test was performed using the `t.test()` function in R, with a significance level of 0.05.

@@

The *t*-test revealed a significant difference in bill lengths between male and female penguins ($t(`r round(t_test_result$parameter, digits = 2)`) = `r round(t_test_result$statistic, digits = 2)`{,}\> p `r format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `r round(mean(blm_female), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `r round(mean(blm_male), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).
